Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-11-12 SupportingInformation.Rmd
adding tinytex library command

```{r tab_aphid_info, echo=F, results='asis',message=F}
library(tibble)
aphid_info <- tibble(c("Apple grass aphid","Bird cherry oat aphid","Black bean aphid","Blackberry cereal aphid","Blackcurrant sowthistle aphid",
           "Corn leaf aphid","Currant lettuce aphid","Damson hop aphid","Grain aphid","Green spruce aphid",
           "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach potato aphid",
           "Potato aphid","Rose grain aphid","Shallot aphid","Sycamore aphid","Willow carrot aphid"),
           c("Rhopalosiphum insertum", "Rhopalosiphum padi", "Aphis fabae", "Sitobion fragariae", "Hyperomyzus lactucae",
             "Rhopalosiphum maidis", "Nasonovia ribisnigri","Phorodon humuli","Sitobion avenae","Elatobium abietinum",
             "Brachycaudus helichrysi","Brevicoryne brassicae","Hyalopterus pruni","Acyrthosiphon pisum","Myzus persicae",
             "Macrosiphum euphorbiae","Metopolophium dirhodum","Myzus ascalonicus","Drepanosiphum platanoidis","Cavariella aegopodii")
)
knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids commonly found across UK \\label{tab_aphid_info}",
      col.names = c("Common name", "Latin binomial"))
```

>>>>

```{r tab_aphid_info, echo=F, results='asis',message=F}
library(tibble)
aphid_info <- tibble(c1=c("Apple grass aphid","Bird cherry oat aphid","Black bean aphid","Blackberry cereal aphid","Blackcurrant sowthistle aphid",
                       "Corn leaf aphid","Currant lettuce aphid","Damson hop aphid","Grain aphid","Green spruce aphid",
                       "Leaf-curling plum aphid","Mealy cabbage aphid","Mealy plum aphid","Pea aphid","Peach potato aphid",
                       "Potato aphid","Rose grain aphid","Shallot aphid","Sycamore aphid","Willow carrot aphid"),
                     c2=c("Rhopalosiphum insertum", "Rhopalosiphum padi", "Aphis fabae", "Sitobion fragariae", "Hyperomyzus lactucae",
                       "Rhopalosiphum maidis", "Nasonovia ribisnigri","Phorodon humuli","Sitobion avenae","Elatobium abietinum",
                       "Brachycaudus helichrysi","Brevicoryne brassicae","Hyalopterus pruni","Acyrthosiphon pisum","Myzus persicae",
                       "Macrosiphum euphorbiae","Metopolophium dirhodum","Myzus ascalonicus","Drepanosiphum platanoidis","Cavariella aegopodii")
)
knitr::kable(aphid_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 20 aphids commonly found across UK \\label{tab_aphid_info}",
      col.names = c("Common name", "Latin binomial"))
```
